bad forecast good decision

### 2020-07-08 notebook/bad-forecast-good-decision.Rmd
maintain names on models

models <- list(f1 = f1, f2 = f2, f3 = f3)

@@

model_sigmas <- c(sigma_g, sigma_g, sigma_g)
transitions <- lapply(seq_along(models), function(i) transition_matrices(models[[i]], states, actions, model_sigmas[[i]]))

>>>>

models <- list(f1 = f1, f2 = f2, f3 = f3)
model_sigmas <- c(sigma_g, sigma_g, sigma_g)

@@

transitions <- lapply(seq_along(models), 
                      function(i) transition_matrices(models[[i]], 
                                                      states, 
                                                      actions, 
                                                      model_sigmas[[i]]))
names(transitions) <- c("f1", "f2", "f3")
